Beyond Ultra-Diffuse Galaxies I: Mass-Size Outliers Among the Satellites of Milky Way Analogs

### 2022-10-22 paper1.tex
fixed bug
Updates from Overleaf
a new deblending figure and new text

%% The default is a single spaced, 10 point font, single spaced article.
%% There are 5 other style options available via an optional argument. They
%% can be invoked like this:
%%
%% \documentclass[arguments]{aastex631}
%% 
%% where the layout options are:
%%
%%  twocolumn   : two text columns, 10 point font, single spaced article.
%%                This is the most compact and represent the final published
%%                derived PDF copy of the accepted manuscript from the publisher
%%  manuscript  : one text column, 12 point font, double spaced article.
%%  preprint    : one text column, 12 point font, single spaced article.  
%%  preprint2   : two text columns, 12 point font, single spaced article.
%%  modern      : a stylish, single text column, 12 point font, article with
%% 		  wider left and right margins. This uses the Daniel
%% 		  Foreman-Mackey and David Hogg design.
%%  RNAAS       : Supresses an abstract. Originally for RNAAS manuscripts 
%%                but now that abstracts are required this is obsolete for
%%                AAS Journals. Authors might need it for other reasons. DO NOT
%%                use \begin{abstract} and \end{abstract} with this style.
%%
%% Note that you can submit to the AAS Journals in any of these 6 styles.
%%
%% There are other optional arguments one can invoke to allow other stylistic
%% actions. The available options are:
%%
%%   astrosymb    : Loads Astrosymb font and define \astrocommands. 
%%   tighten      : Makes baselineskip slightly smaller, only works with 
%%                  the twocolumn substyle.
%%   times        : uses times font instead of the default
%%   linenumbers  : turn on lineno package.
%%   trackchanges : required to see the revision mark up and print its output
%%   longauthor   : Do not use the more compressed footnote style (default) for 
%%                  the author/collaboration/affiliations. Instead print all
%%                  affiliation information after each name. Creates a much 
%%                  longer author list but may be desirable for short 
%%                  author papers.
%% twocolappendix : make 2 column appendix.
%%   anonymous    : Do not show the authors, affiliations and acknowledgments 
%%                  for dual anonymous review.
%%
%% these can be used in any combination, e.g.
%%
%% \documentclass[twocolumn,linenumbers,trackchanges]{aastex631}
%%
%% AASTeX v6.* now includes \hyperref support. While we have built in specific
%% defaults into the classfile you can manually override them with the
%% \hypersetup command. For example,
%%
%% \hypersetup{linkcolor=red,citecolor=green,filecolor=cyan,urlcolor=magenta}
%%
%% will change the color of the internal links to red, the links to the
%% bibliography to green, the file links to cyan, and the external links to
%% magenta. Additional information on \hyperref options can be found here:
%% https://www.tug.org/applications/hyperref/manual.html#x1-40003
%%
%% Note that in v6.3 "bookmarks" has been changed to "true" in hyperref
%% to improve the accessibility of the compiled pdf file.
%%
%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
% \newcommand{\sbunit}{mag~arcsec$^{-2}$}
\newcommand{\sbunit}{\mathrm{mag\ arcsec}^{-2}}
\newcommand{\sbcen}{\mu_{0}(g)}
\newcommand{\sbeff}{\overline{\mu}_{\mathrm{eff}}(g)}
\newcommand{\sbeffr}{\overline{\mu}_{\mathrm{eff}}(r)}
\newcommand{\jiaxuan}[1]{\textcolor{orange}{\textbf{Jiaxuan: #1}}}

@@

\shorttitle{Mass-size outliers in MW satellites}
\shortauthors{Li et al.}
%%
%% You can add a light gray and diagonal water-mark to the first page 
%% with this command:
%% \watermark{text}
%% where "text", e.g. DRAFT, is the text to appear.  If the text is 
%% long you can control the water-mark size with:
%% \setwatermarkfontsize{dimension}
%% where dimension is any recognized LaTeX dimension, e.g. pt, in, etc.
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\graphicspath{{./}{figures/}}
%% This is the end of the preamble.  Indicate the beginning of the
%% manuscript itself with \begin{document}.

@@

\author[0000-0002-1841-2252]{Rachael Beaton}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\author[0000-0002-2991-9]{Kirsten Casey}
\affiliation{Center for Cosmology and AstroParticle Physics (CCAPP), The Ohio State University, Columbus, OH 43210, USA}
\author[0000-0002-1841-2252]{Shany Danieli}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\author[0000-0002-1841-2252]{Andy Goulding}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\author[0000-0002-2704-5028]{Remy Joseph}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\affiliation{Oskar Klein Centre for Cosmoparticle Physics, Department of Physics, Stockholm University, Stockholm SE-106 91, Sweden}
\author[0000-0002-1841-2252]{Erin Kado-Fong}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}

\author[0000-0002-1418-3309]{Ji Hoon Kim}
\affiliation{Astronomy Program, Department of Physics and Astronomy, Seoul National University, 1 Gwanak-ro, Gwanak-gu, Seoul 08826, Republic of Korea}
\affiliation{SNU Astronomy Research Center, Seoul National University, 1 Gwanak-ro, Gwanak-gu, Seoul 08826, Republic of Korea}
\author{Lauren MacArthur}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}

%% Note that the \and command from previous versions of AASTeX is now
%% depreciated in this version as it is no longer necessary. AASTeX 
%% automatically takes care of all commas and "and"s between authors names.

%% AASTeX 6.31 has the new \collaboration and \nocollaboration commands to
%% provide the collaboration status of a group of authors. These commands 
%% can be used either before or after the list of corresponding authors. The
%% argument for \collaboration is the collaboration identifier. Authors are
%% encouraged to surround collaboration identifiers with ()s. The 
%% \nocollaboration command takes no argument and exists to indicate that
%% the nearby authors are not part of surrounding collaborations.

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
Large diffuse galaxies are hard to find, but understanding the environments where they live and their numbers, and ultimately their origins, is of intense interest and important for galaxy formation and evolution. Using the Hyper Suprime-Cam data, we perform a systematic search for low surface-brightness galaxies and present novel and effective methods for detecting and modeling them. 
As a case study, we build a statistical sample of galaxies that are outliers in the mass-size relation and are satellites of Milky Way analogs in the nearby Universe ($0.01 < z < 0.04$). These ``ultra-puffy'' galaxies (UPGs), defined to be $1.5\sigma$ above the average mass-size relation, better represents the tail of satellite size distribution. We find that each MW analog hosts $N_{\rm UPG} = 0.61\pm 0.04$ ultra-puffy galaxies on average, which is comparable to the observed abundance at this halo mass in the Local Volume. We also construct a sample of ultra-diffuse galaxies (UDGs) in MW analogs and find an abundance of $N_{\rm UDG} = 0.76\pm0.04$ per host. We compare with literature results including UDG searches in clusters and massive groups. The UDG abundance scales with the host halo mass following a sublinear power law. We argue that our definition for ultra-puffy galaxies, which is based on the mass-size relation, is more physically-motivated and objective than the common definition of ultra-diffuse galaxies, which depends on a surface brightness cut and thus yields different surface mass density cuts for quenched and star-forming galaxies. 
\end{abstract}

@@

\section{Introduction} \label{sec:intro}
In a variety of galaxies in the Universe, there is an interesting subset of galaxies with low surface brightness and large physical size \citep[dubbed low surface brightness galaxies or LSBGs, e.g.,][]{Sandage1984,Caldwell1987,Impey1988,McGaugh1995,Dalcanton1997a}. Recently, new excitement has been generated by the discovery of a large population of ultra-diffuse galaxies (UDGs) in the Coma cluster \citep{vanDokkum2015}, accompanied by many other works on detecting UDGs in clusters \citep[e.g.,][]{Koda2015,Mihos2015,Yagi2016,vdBurg2016,vdBurg2017,Lee2017,ManceraPina2018,Zaritsky2019}, groups \citep[e.g.,][]{Roman2017b,Greco2018,SAGA-II,CarlstenELVES2022}, and the field \citep[e.g.,][]{Leisman2017,Roman2019,Prole2019,Tanoglidis2021,Kadowaki2021}. There have been a variety of studies of these diffuse galaxy systems, ranging from their dark matter content \citep[e.g.,][]{Mowla2017,vanDokkum2018,vanDokkum2019,Wasserman2019,Keim2022}, to their globular cluster populations \citep[e.g.,][]{vanDokkum2017,Somalwar2020,Forbes2020,Danieli2022,Gannon2022,vanDokkum2022GC}, and their stellar populations \citep[e.g.,][]{Gu2018,Ferre-Mateu2018,Villaume2022}. UDGs are defined to be galaxies with large size ($r_e > 1.5$ kpc) and low surface brightness ($\sbcen > 24.0\ \sbunit$), and thus UDGs are outliers in size and surface brightness for their stellar mass compared to normal dwarf galaxies. A central question about LSBGs, including UDGs, is what causes them to be outliers from the average mass-size relation of dwarf galaxies?
% Therefore, a central question about mass-size outliers including UDGs is what physical mechanisms are responsible for the formation and quenching of these large diffuse galaxies.

Various mechanisms have been proposed to explain the presence of large, diffuse galaxies (as mass-size outliers) across different environments. In the field (i.e, in isolation), their large sizes might be caused by stellar feedback \citep{DiCintio2017,Chan2018}, early galaxy mergers \citep{Wright2021}, passing into and out of a more massive halo (so-called backsplash satellites, \citealt{Benavides2021}), or by inhabiting halos with higher spin \citep{Dalcanton1997,Amorisco2016,Liao2019,Benavides2022}. In groups and clusters, their large sizes may ensue from tidal heating near pericenter \citep{Jiang2019}, via adiabatic expansion due to mass loss \citep{Tremmel2020}, or even via a bullet-dwarf collision \citep{vandokkum2022Nat,vanDokkum2022GC}. Despite theoretical advances, it is still an open question how mass-size outliers like UDGs are formed and quenched. It is also unclear whether mass-size outliers belong to a distinct class of galaxies or are just a natural extension of dwarf systems to lower surface brightness or larger size. A nice way to to answer these questions is to compare these mass-size outliers with ``normal'' low mass galaxies for which we have a better understanding.

Our best understanding of the low mass galaxy regime comes from the satellite system of our Milky Way (MW) and the Local Group (LG) \citep[e.g.,][]{McConnachie2012,Simon2019}. With the advent of deep sky surveys and dedicated spectroscopic programs, we are now in a position to also map the satellite systems of MW analogs in the Local Volume and nearby Universe. The Satellites Around Galactic Analogs (SAGA) survey is designed to spectroscopically confirm the satellites of 100 MW analogs at 20--40 Mpc \citep{SAGA-I,SAGA-II}. The Exploration of Local VolumE Satellites (ELVES,  \citealt{ELVES-I,ELVES-II,CarlstenELVES2022}) survey uses deep imaging data to identify satellite candidates of MW-like hosts in the Local Volume (LV, $D<12$ Mpc) and estimate surface brightness fluctuation distances from images to confirm their association with their hosts. Having these MW satellites as a reference frame, we can contrast them with the mass-size outliers in the same environment to understand the formation of large diffuse galaxies. However, there are only $\sim 40$ confirmed UDGs associated with MW analogs in the literature \citep{Roman2017b,Cohen2018,SAGA-II,CarlstenELVES2022,Karunakaran2022b}. Therefore, a larger sample of mass-size outliers associated with MW-like hosts is needed to conduct such a comparison between the mass-size outliers and the normal satellites.

@@

\section{Data} \label{sec:data}
\subsection{Hyper Suprime-Cam Subaru Strategic Program}
The Hyper Suprime-Cam Subaru Strategic Program (HSC-SSP, \citealt{Aihara2018}; hereafter the HSC survey)\footnote{\url{https://hsc-release.mtk.nao.ac.jp/doc/}} is an optical imaging survey using the 8.2-m Subaru telescope and the Hyper Suprime-Camera \citep{Miyazaki2012, Miyazaki2018}. The \texttt{Wide} layer is designed to cover $\sim 1000\ \rm{deg}^{2}$ of the sky in five broad bands ($grizy$), reaching a depth of $g=26.6$ mag, $r=26.2$ mag and $i=26.2$ mag ($5\sigma$ point source detection). HSC data are processed using the \code{hscPipe}\footnote{\url{https://hsc.mtk.nao.ac.jp/pipedoc_e/}} \citep{Bosch2018}, which is a customized version of the Legacy Survey of Space and Time (LSST) pipeline \citep{LSST-pipeline}\footnote{\url{https://pipelines.lsst.io/}}.

@@

\subsection{NASA-Sloan Atlas}
We use the NASA-Sloan Atlas (NSA\footnote{\url{http://nsatlas.org}}, \citealt{Blanton2005,Blanton2011}) to select galaxies that are analogous to our Milky Way based on their stellar mass (see \S\ref{sec:match}), then we match the LSBGs to these MW analogs. The NSA catalog provides various physical properties of galaxies in the nearby Universe as derived from the Sloan Digital Sky Survey \citep[SDSS,][]{York2000}. We use the most recent version of the NSA catalog (\code{v1\_0\_1}\footnote{\url{https://www.sdss.org/dr13/manga/manga-target-selection/nsa/}}) which contains about $640,000$ galaxies out to $z < 0.15$. This version also updates the aperture photometry to elliptical Petrosian photometry since it is considered to be more reliable than the photometry used in the older versions. In this paper, we use the stellar mass derived from elliptical Petrosian photometry using \code{kcorrect v4\_2} \citep{Blanton2007}. The redshifts of galaxies in NSA come from several spectroscopic surveys, \ion{H}{1} gas surveys, or direct distance measurements.

@@

Continuing the work in \citet{Greco2018} (hereafter \citetalias{Greco2018}), we conduct a systematic search for low surface brightness galaxies (LSBGs) in the HSC PDR2 data, which covers $\sim 1.5$ times the sky area of \citetalias{Greco2018}. The schematic of the searching method in this paper remains similar to that in \citetalias{Greco2018}, but we do improve the searching completeness and purity by adding several new steps, which are highlighted in this section. We outline the major steps below and refer the reader who are already familiar with the algorithms in LSBG searches to \S \ref{sec:sample_construction} for UDG and UPG sample construction.

\begin{enumerate}
    \item Source Detection (\S \ref{sec:detection}): we run \href{https://www.astromatic.net/software/sextractor/}{\code{SourceExtractor}} \citep{Bertin1996} on the coadd images after removing bright extended sources. Then we apply an initial size and color cut based on the output catalog. 
    \item Deblending (\S \ref{sec:deblending}): we remove false positives that are not likely to be LSBGs by running \href{https://pmelchior.github.io/scarlet/}{\code{scarlet}} \citep{Melchior2018}. We use the \code{scarlet} models to define color-size-morphology-surface brightness cuts. This step removes roughly 97\% of false positives.
    \item Modeling (\S \ref{sec:modeling}): we fit a parametric model to the LSBGs to estimate their structural parameters. 
    \item Completeness and measurement uncertainties (\S \ref{sec:comp_meas}) are characterized by injecting mock \sersic{} galaxies into images. 
\end{enumerate}
The number of objects remained after each step is shown in Table \ref{tab:steps_flow}. Our source detection pipeline \code{hugs}\footnote{\url{https://github.com/johnnygreco/hugs}} and deblending and modeling code \code{kuaizi}\footnote{\url{https://github.com/AstroJacobLi/kuaizi}} are open-sourced and available online.

@@

\subsection{Source Detection}\label{sec:detection}
\citetalias{Greco2018} performed a search for LSBGs in the first $\sim 200$ deg$^2$ of the HSC survey and uncovered 781 LSBGs. We continue the work in \citetalias{Greco2018} and extend the search to the HSC PDR2 data, which covers $\sim 300\ \rm{deg}^{2}$ and has much better sky subtraction for LSB studies compared to previous data releases. We follow the same method for source detection as in \citetalias{Greco2018}, but make several updates to accommodate PDR2 data. These updates are guided by both our understanding of PDR2 data and completeness tests using mock galaxies. We summarize the main steps of LSBG search method here, and refer the interested readers to \citetalias{Greco2018} and Appendix \ref{ap:detection} for more details. 
% In the following, we summarize the main steps of the search and emphasize the updates made to improve the overall completeness and purity. We refer the interested readers to \citetalias{Greco2018} for more details.

We start by replacing the bright sources and their associated LSB outskirts with the sky noise. Bright objects and their diffuse light are identified using surface brightness thresholding. Then we run a detection using \href{https://sep.readthedocs.io/en/v1.1.x}{\code{sep}} \citep{Barbary2016} to remove small compact sources and noisy peaks and also replace their footprints with sky noise. We use \code{SourceExtractor} to detect sources on the ``cleaned'' images with a low detection threshold. Taking the output catalog from \code{SourceExtractor}, we apply an initial selection based on the size, color, and peakiness of objects.

@@

\begin{figure*}
	\vbox{ 
		%\vskip -10mm
		\centering
		\includegraphics[width=1\linewidth]{vanilla_scarlet_demo.pdf}
		\includegraphics[width=1\linewidth]{vanilla_scarlet_demo2.pdf}
	}
	\caption{A demonstration of the deblending step as described in \S\ref{sec:deblending} and \S\ref{ap:deblending}. Here we show two objects from our initial sample: the one shown in the top panels is a blue LSBG, whereas the one shown in the bottom is a false positive detection which is a blend between high-$z$ galaxy and galaxy outskirts. The first columns show the $griz$ color-composite images with the bounding boxes overlaid. The objects covered by the gray shades are masked during fitting. The remaining columns show the initial model, optimized models (PSF convolved), residual image, and the optimized model of the target galaxy only. 
	}
	\label{fig:vanilla_scarlet_demo}
\end{figure*}

@@

We use vanilla \code{scarlet} to model the LSBG candidate and extract structural and morphological parameters from the \code{scarlet} model, which are further used to exclude false positives from our LSBG sample. In the following subsections, we briefly describe how we detect peaks on the image, initialize and optimize \code{scarlet} models. We refer the readers to Appendix \ref{ap:deblending} for more detailed descriptions.

@@

We notice that the optimized model of the blue LSBG captures its color and morphology quite well. For the false-positive case, the optimized model has a notable bright background thanks to the flat-sky component, and the model for the target itself is very red and compact. The reason why it passes our initial selection is that the galaxy outskirts are shredded by \code{SourceExtractor} and happen to have a large size and the right color. But once modeled using \code{scarlet}, it becomes clear that this is just a false positive detection and should be removed. A rubric based on the \code{scarlet} model is therefore needed to help us exclude the false positives.

@@

We also use the Gini-M20 and CAS statistics. The Gini coefficient and M20 statistics \citep{Abraham2003,Lotz2004} quantify how concentrated/extended the flux distribution is across the image. The CAS statistics characterize the concentration $C$, asymmetry $A$, and smoothness $S$ of the light distribution of the object. We refer the reader to \citet{statmorph} for more details on their definitions and implementations. We measure the morphological and structural parameters in $g$-band. %The morphological and structural parameters are the same in different bands by construction in the \code{scarlet} model.

>>>>

%%
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
% \newcommand{\sbunit}{mag~arcsec$^{-2}$}
\newcommand{\sbunit}{\mathrm{mag\ arcsec}^{-2}}
\newcommand{\sbcen}{\mu_{0}(g)}
\newcommand{\sbeff}{\overline{\mu}_{\mathrm{eff}}(g)}
\newcommand{\sbeffr}{\overline{\mu}_{\mathrm{eff}}(r)}
\newcommand{\jiaxuan}[1]{\textcolor{orange}{\textbf{Jiaxuan: #1}}}

@@

\shorttitle{Mass-size outliers among MW satellites}
\shortauthors{Li et al.}
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\graphicspath{{./}{figures/}}
%% This is the end of the preamble.  Indicate the beginning of the
%% manuscript itself with \begin{document}.

@@

\author[0000-0002-1841-2252]{Rachael Beaton}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\author[0000-0002-2991-9251]{Kirsten Casey}
\affiliation{Center for Cosmology and AstroParticle Physics (CCAPP), The Ohio State University, Columbus, OH 43210, USA}
\author[0000-0002-1841-2252]{Shany Danieli}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\author[0000-0002-1841-2252]{Andy Goulding}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\author[0000-0002-2704-5028]{Remy Joseph}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\affiliation{Oskar Klein Centre for Cosmoparticle Physics, Department of Physics, Stockholm University, Stockholm SE-106 91, Sweden}
\author[0000-0002-1841-2252]{Erin Kado-Fong}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}

\author[0000-0002-1418-3309]{Ji Hoon Kim}
\affiliation{Astronomy Program, Department of Physics and Astronomy, Seoul National University, 1 Gwanak-ro, Gwanak-gu, Seoul 08826, Republic of Korea}
\affiliation{SNU Astronomy Research Center, Seoul National University, 1 Gwanak-ro, Gwanak-gu, Seoul 08826, Republic of Korea}

\author{Lauren A. MacArthur}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
Large diffuse galaxies are hard to find, but understanding the environments where they live and their numbers, and ultimately their origins, is of intense interest and important for galaxy formation and evolution. Using Subaru's Hyper Suprime-Cam Strategic Survey Program data, we perform a systematic search for low surface-brightness galaxies and present novel and effective methods for detecting and modeling them. 
As a case study, we build a statistical sample of galaxies that are outliers in the mass-size relation and are satellites of Milky Way analogs in the nearby Universe ($0.01 < z < 0.04$). These ``ultra-puffy'' galaxies (UPGs), defined to be $1.5\sigma$ above the average mass-size relation, represents the tail of the satellite size distribution. We find that each MW analog hosts $N_{\rm UPG} = 0.61\pm 0.04$ ultra-puffy galaxies on average, which is comparable to the observed abundance at this halo mass in the Local Volume. We also construct a sample of ultra-diffuse galaxies (UDGs) in MW analogs and find an abundance of $N_{\rm UDG} = 0.76\pm0.04$ per host. With literature results, we confirm that the UDG abundance scales with the host halo mass following a sublinear power law. We argue that our definition for ultra-puffy galaxies, which is based on the mass-size relation, is more physically-motivated than the common definition of ultra-diffuse galaxies, which depends on an arbitrary surface brightness cut and thus yields different surface mass density cuts for quenched and star-forming galaxies. 
\end{abstract}

@@

\section{Introduction} \label{sec:intro}
In a variety of galaxies in the Universe, there is an interesting subset of galaxies with low surface brightness and large physical size \citep[dubbed low surface brightness galaxies or LSBGs, e.g.,][]{Sandage1984,Caldwell1987,Impey1988,McGaugh1995,Dalcanton1997a}. Recently, new excitement has been generated by the discovery of a large population of ultra-diffuse galaxies (UDGs) in the Coma cluster \citep{vanDokkum2015}, accompanied by many other works on detecting UDGs in clusters \citep[e.g.,][]{Koda2015,Mihos2015,Yagi2016,vdBurg2016,vdBurg2017,Lee2017,ManceraPina2018,Zaritsky2019}, groups \citep[e.g.,][]{Roman2017b,Greco2018,SAGA-II,CarlstenELVES2022}, and the field \citep[e.g.,][]{Leisman2017,Roman2019,Prole2019,Tanoglidis2021,Kadowaki2021}. There have been a variety of studies of these diffuse galaxy systems, ranging from their dark matter content \citep[e.g.,][]{Mowla2017,vanDokkum2018,vanDokkum2019,Wasserman2019,Keim2022}, to their globular cluster populations \citep[e.g.,][]{vanDokkum2017,Somalwar2020,Forbes2020,Danieli2022,Gannon2022,vanDokkum2022GC}, and their stellar populations \citep[e.g.,][]{Gu2018,Ferre-Mateu2018,Villaume2022}. UDGs are defined to be galaxies with large size ($r_e > 1.5$ kpc) and low surface brightness ($\sbcen > 24.0\ \sbunit$), and thus UDGs are outliers in size and surface brightness for their stellar mass compared to normal dwarf galaxies. A central question about LSBGs, including UDGs, is what causes them to be outliers from the average mass-size relation of dwarf galaxies?

Various mechanisms have been proposed to explain the presence of large, diffuse galaxies (as mass-size outliers) across different environments. In the field (i.e, in isolation), their large sizes might be caused by stellar feedback \citep{DiCintio2017,Chan2018}, early galaxy mergers \citep{Wright2021}, passing into and out of a more massive halo (so-called backsplash satellites, \citealt{Benavides2021}), or by inhabiting halos with higher spin \citep{Dalcanton1997,Amorisco2016,Liao2019,Benavides2022}. In groups and clusters, their large sizes may ensue from tidal heating near pericenter \citep{Jiang2019}, via adiabatic expansion due to mass loss \citep{Tremmel2020}, or even via a bullet-dwarf collision \citep{vandokkum2022Nat,vanDokkum2022GC}. Despite theoretical advances, it is still an open question how mass-size outliers like UDGs are formed and quenched. It is also unclear whether mass-size outliers belong to a distinct class of galaxies or are just a natural extension of dwarf systems to lower surface brightness or larger size. A nice way to to answer these questions is to compare these mass-size outliers with ``normal'' low mass galaxies which have been studied extensively.

Our best understanding of the low mass galaxy regime comes from the satellite system of our Milky Way (MW) and the Local Group (LG) \citep[e.g.,][]{McConnachie2012,Simon2019}. With the advent of deep sky surveys and dedicated spectroscopic programs, we are now in a position to also map the satellite systems of MW analogs (typically defined as galaxies having similar stellar mass or halo mass to MW) in the Local Volume and nearby Universe. The Satellites Around Galactic Analogs (SAGA) survey is designed to spectroscopically confirm the satellites of 100 MW analogs at 20--40 Mpc \citep{SAGA-I,SAGA-II}. The Exploration of Local VolumE Satellites (ELVES,  \citealt{ELVES-I,ELVES-II,CarlstenELVES2022}) survey uses deep imaging data to identify satellite candidates of MW-like hosts in the Local Volume (LV, $D<12$ Mpc) and estimate surface brightness fluctuation distances from images to confirm their association with their hosts. Having these MW satellites as a reference frame, we can contrast them with the mass-size outliers in the same environment to understand the formation of large diffuse galaxies. However, there are only $\sim 40$ confirmed UDGs associated with MW analogs in the literature \citep{Roman2017b,Cohen2018,SAGA-II,CarlstenELVES2022,Karunakaran2022b}. Therefore, a larger sample of mass-size outliers associated with MW-like hosts is needed to conduct such a comparison between the mass-size outliers and the normal satellites.

@@

\section{Data} \label{sec:data}
\subsection{Hyper Suprime-Cam Subaru Strategic Program}
The Hyper Suprime-Cam Subaru Strategic Program (HSC-SSP, \citealt{Aihara2018}; hereafter the HSC survey)\footnote{\url{https://hsc-release.mtk.nao.ac.jp/doc/}} is an optical imaging survey using the 8.2-m Subaru telescope and the Hyper Suprime-Camera \citep{Miyazaki2012, Miyazaki2018}. The \texttt{Wide} layer is designed to cover $\sim 1000\ \rm{deg}^{2}$ of the sky in five broad bands ($grizy$), reaching a depth of $g=26.6$ mag, $r=26.2$ mag and $i=26.2$ mag ($5\sigma$ point source detection). HSC data are processed using the \code{hscPipe}\footnote{\url{https://hsc.mtk.nao.ac.jp/pipedoc_e/}} \citep{Bosch2018}, which is a customized version of the Vera Rubin Observatory Legacy Survey of Space and Time (LSST) pipeline \citep{LSST-pipeline}\footnote{\url{https://pipelines.lsst.io/}}.

@@

\subsection{NASA-Sloan Atlas}
We use the NASA-Sloan Atlas (NSA\footnote{\url{http://nsatlas.org}}, \citealt{Blanton2005,Blanton2011}) to select galaxies that are analogous to our Milky Way based on their stellar mass (see \S\ref{sec:match}), then we match the LSBGs to these MW analogs. The NSA catalog provides various physical properties of galaxies in the nearby Universe as derived from the Sloan Digital Sky Survey \citep[SDSS,][]{York2000}. We use the most recent version of the NSA catalog (\code{v1\_0\_1}\footnote{\url{https://www.sdss.org/dr13/manga/manga-target-selection/nsa/}}) which contains about $640,000$ galaxies out to $z < 0.15$. This version also updates the aperture photometry to elliptical Petrosian photometry since it is considered to be more reliable than the photometry used in the older versions. In this paper, we use the stellar masses derived from the elliptical Petrosian photometry using \code{kcorrect v4\_2} \citep{Blanton2007}. The redshifts of the galaxies in NSA come from several spectroscopic surveys, \ion{H}{1} gas surveys, or direct distance measurements.

@@

Continuing the work of \citet{Greco2018} (hereafter \citetalias{Greco2018}), we conduct a systematic search for low surface brightness galaxies (LSBGs) in the HSC PDR2 data, which covers $\sim 1.5$ times the sky area of \citetalias{Greco2018}. The schematic of the searching method in this paper remains similar to that in \citetalias{Greco2018}, but we do improve the search completeness and purity by adding several new steps, which are highlighted in this section. We outline the major steps below and refer the reader who are already familiar with the algorithms in LSBG searches to \S \ref{sec:sample_construction} for the UDG and UPG sample construction.

\begin{enumerate}
    \item Source Detection (\S \ref{sec:detection}): we run \href{https://www.astromatic.net/software/sextractor/}{\code{SourceExtractor}} \citep{Bertin1996} on the coadd images after removing bright extended sources. Then we apply an initial size and color cut based on the output catalog. 
    \item Deblending (\S \ref{sec:deblending}): we remove false positives that are not likely to be LSBGs by running \href{https://pmelchior.github.io/scarlet/}{\code{scarlet}} \citep{Melchior2018}. We use the \code{scarlet} models to define color-size-morphology-surface brightness cuts. This step removes roughly 97\% of false positives.
    \item Modeling (\S \ref{sec:modeling}): we fit a parametric model to the LSBGs to estimate their structural parameters. 
    \item Completeness and measurement uncertainties (\S \ref{sec:comp_meas}) are characterized by injecting mock \sersic{} galaxies into images. 
\end{enumerate}
The number of objects remaining after each step is shown in Table \ref{tab:steps_flow}. Our source detection pipeline \code{hugs}\footnote{\url{https://github.com/johnnygreco/hugs}} and the deblending and modeling code \code{kuaizi}\footnote{\url{https://github.com/AstroJacobLi/kuaizi}} are open-sourced and available online.

@@

\subsection{Source Detection}\label{sec:detection}
\citetalias{Greco2018} performed a search for LSBGs in the first $\sim 200$ deg$^2$ of the HSC survey and uncovered 781 LSBGs. We continue the work in \citetalias{Greco2018} and extend the search to the HSC PDR2 data, which covers $\sim 300\ \rm{deg}^{2}$ and has a sky subtraction better suited for LSB studies compared to previous data releases. We follow the same method for source detection as in \citetalias{Greco2018}, but make several updates to accommodate the PDR2 data. These updates are guided by both our understanding of PDR2 data and completeness tests using mock galaxies. We summarize the main steps of the LSBG search method here, and refer the interested reader to \citetalias{Greco2018} and Appendix \ref{ap:detection} for more details. 
% In the following, we summarize the main steps of the search and emphasize the updates made to improve the overall completeness and purity. We refer the interested readers to \citetalias{Greco2018} for more details.

We start by replacing the bright sources and their associated LSB outskirts with the sky noise. Bright objects and their diffuse light are identified using surface brightness thresholding. Then we run a detection using \href{https://sep.readthedocs.io/en/v1.1.x}{\code{sep}} \citep{Barbary2016} to remove small compact sources and noisy peaks and replace their footprints with sky noise. We use \code{SourceExtractor} to detect sources on the ``cleaned'' images with a low detection threshold. Taking the output catalog from \code{SourceExtractor}, we apply an initial selection based on the size, color, and peakiness of objects.

@@

\begin{figure*}
	\vbox{ 
		%\vskip -10mm
		\centering
		\includegraphics[width=1\linewidth]{vanilla_scarlet_demo.pdf}
		\includegraphics[width=1\linewidth]{vanilla_scarlet_demo2.pdf}
	}
	\caption{A demonstration of the deblending step as described in \S\ref{sec:deblending} and \S\ref{ap:deblending}. Here we show two objects from our initial sample: the one shown in the top panels is a blue LSBG, whereas the one shown in the bottom is a false positive detection which is a blend between high-$z$ galaxy and galaxy outskirts. The first columns show the $griz$ color-composite images with the bounding boxes overlaid. The objects covered by the gray shades are masked during fitting. The remaining columns show the initial model, the optimized model (PSF convolved), the residual image, and the optimized model of the target galaxy only. 
	}
	\label{fig:vanilla_scarlet_demo}
\end{figure*}

@@

We use vanilla \code{scarlet} to model the LSBG candidate and the structural and morphological parameters are then used to exclude false positives from our LSBG sample. In the following subsections, we briefly describe how we detect peaks on the image to initialize and optimize \code{scarlet} models. We refer the readers to Appendix \ref{ap:deblending} for a more detailed description.

@@

We notice that the optimized model of the blue LSBG captures its color and morphology quite well. For the false-positive case, the optimized model has a notable bright background thanks to the flat-sky component, and the model for the target itself is very red and compact. It passes our initial selection because the galaxy outskirts are shredded by \code{SourceExtractor} and happen to have a large size and similar color to our LSB galaxies. But once modeled using \code{scarlet}, it becomes clear that this is just a false positive detection and should be removed. A rubric based on the \code{scarlet} model is therefore needed to help us identify and exclude the false positives.

@@

We also use the Gini-M20 and CAS statistics. The Gini coefficient and M20 statistics \citep{Abraham2003,Lotz2004} quantify how concentrated/extended the flux distribution is across the image. The CAS statistics characterize the concentration $C$, asymmetry $A$, and smoothness $S$ of the light distribution of the object. We refer the reader to \citet{statmorph} for more details on their definitions and implementations. We measure the morphological and structural parameters in $g$-band.
